%-------------------------
% Resume in Latex
% Author : Aras Gungore
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome5}
\input{glyphtounicode}


%---------- FONT OPTIONS ----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}


\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSubSubheading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeEducationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \text{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeOrganizationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
      \textit{\small#3}
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{0pt}}

\newcommand{\faSkill}[1]{%
   \makebox[1.25em][l]{%
      \csname fa#1\endcsname   
   }%
}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\hypersetup{
	pdftitle = {Michael Hennelly - Software Engineer}
}


\begin{document}

%---------- HEADING ----------

\begin{center}
    \textbf{\Huge \scshape Michael Hennelly}\\ \vspace{3pt}
    \faEnvelope \hspace{.5pt} \href{mailto:mike@mhennelly.com}{\texttt{mike@mhennelly.com}}
    $|$
    \faLinkedin \hspace{.5pt} \href{https://www.linkedin.com/in/MHennelly}{\texttt{LinkedIn}}
    $|$
    \faGithub \hspace{.5pt} \href{https://github.com/mhnnlly}{\texttt{GitHub}}
    $|$
    \faGlobeAmericas \hspace{.5pt} \href{https://blog.mhnnlly.com}{\texttt{Website}}
    $|$
    \faMapMarker* \hspace{.5pt}San Francisco, CA
\end{center}

%----------- WORK EXPERIENCE -----------

\section{Experience}
  \vspace{3pt}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Amazon Web Services}{Sunnyvale, CA}
      {Software Development Engineer}{Nov 2022 \textbf{--} Apr 2023}
        \resumeItemListStart
            \resumeItem{Worked on the real-time communication platform Chime SDK.}
            \resumeItem{Developed a resource tagging and analytics service that provides cost and usage breakdowns for tagged resources.}
            \resumeItem{Built a system that handles concurrent writes using a technique similar to optimistic concurrency control.}
            \resumeItem{Built a monitoring system which reports inconsistencies between databases of tagged resources.}
            \resumeItem{Launched the tagging and analytics service in all 10 AWS regions supported by the Chime SDK platform.}
        \resumeItemListEnd
    
    \resumeSubheading
      {Rivian}{Palo Alto, CA}
      {Software Engineer}{Aug 2021 \textbf{--} Aug 2022}
        \resumeItemListStart
            \resumeItem{Worked on the central notification system for Rivian's 114,000+ customers.}
            \resumeItem{Developed email, SMS, and push notification APIs on the serverless framework AWS Chalice.}
            \resumeItem{Built a SMS chat agent that allows customers to opt-in for SMS order updates and get help.}
            \resumeItem{Delivered multi-recipient messaging that works across all message channels.}
            \resumeItem{Delivered notification streams that send hundreds of thousands of events each week to the data warehouse.}
            \resumeItem{Added phone number validation and template rendering endpoints.}
            \resumeItem{Improved customer experience by introducing a message consolidation system which reduces notification volume.}
        \resumeItemListEnd

    \resumeSubheading
      {Meggitt}{Simi Valley, CA}
      {Software Engineer Intern}{Aug 2020 \textbf{--} Dec 2020}
        \resumeItemListStart
            \resumeItem{Developed a business analytics web-application with Chart.js, PHP and MySQL.}
            \resumeItem{Delivered visualization into parts and orders for Meggitt's Simi Valley manufacturing site.}
        \resumeItemListEnd
    
  \resumeSubHeadingListEnd
  
  %----------- PROJECTS -----------

\section{Projects}
    \vspace{3pt}
    \resumeSubHeadingListStart
    
    \resumeProjectHeading
    	{\textbf{Blog} $|$ \href{https://blog.mhnnlly.com}{\texttt{blog.mhnnlly.com}}}{\small{\textit{Dec 2023 -- Present}}}
    	\resumeItemListStart
    		\resumeItem{Writing a personal blog where I discuss things related to tech and creative writing.}
    		\resumeItem{Built with Next.js and Vercel.}
    	\resumeItemListEnd
      
      \resumeProjectHeading
        {\textbf{GraphicsMagick Web API} $|$ \href{https://static.mhennelly.com}{\texttt{static.mhennelly.com}}}{\small{\textit{Mar 2021 \textbf{--} Jun 2021}}}
          \resumeItemListStart
            \resumeItem{Built a web API to the GraphicsMagick image editing suite.}
            \resumeItem{Allows clients to create HTML-embeddable edits of images through URL query parameters.}
            \resumeItem{Documentation and source code are available at \href{https://github.com/mhnnlly/static-magick}{\underline{github.com/mhnnlly/static-magick}}.}
            \resumeItem{Demo of the web API in use available at \href{https://old.mhennelly.com}{\underline{old.mhennelly.com}}.}
          \resumeItemListEnd
      
    \resumeSubHeadingListEnd

%----------- EDUCATION -----------

\section{Education}
  \vspace{3pt}
  \resumeSubHeadingListStart
    \resumeEducationHeading
      {UCLA}{Los Angeles, CA}
      {B.S. Computer Science, 3.7/4.0}{Sep 2018 \textbf{--} Jun 2021}
    \\~\\
    \textit{Coursework}: Software Engineering, Distributed Systems, Algorithms and Complexity, Networking,\\Computer Graphics, Programming Languages, Assembly and Computer Architecture,\\Operating Systems, Data Mining, Artificial Intelligence \\
    
  \resumeSubHeadingListEnd


%----------- SKILLS -----------


\section{Skills}
  \vspace{2pt}
  \resumeSubHeadingListStart
    \small{\item{
		
    
        \faSkill{Python} \textbf{ Languages:}{ Python (1), Java (1), SQL (1), PHP (1), Javascript (2), Typescript (2), C (3), C++ (3) } \\ \vspace{3pt}
        
        \faSkill{React} \textbf{ Frontend:}{ Next.js (2), React (2) } \\ \vspace{3pt}
        
        \faSkill{Server} \textbf{ Backend:}{ AWS Chalice (1), Next.js (2), Flask (3), Express.js (3) } \\ \vspace{3pt}
        
          \faSkill{Cloud} \textbf{ Cloud:}{ AWS (1), Vercel (2) } \\ \vspace{3pt}
        
          \faSkill{Book} \textbf{ Interests:}{ Linux, PyTorch } \\ \vspace{12pt}


        \textbf{Key:}\\
        \\(1) = Used In A Previous Job \hspace{6pt} (2) = Used In A Recent Project \hspace{6pt} (3) = Have Used In The Past
    }}
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
